\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip

### 2015-03-05 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
Some typos fixes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64806 15284696-431f-4ddb-bdfa-cd5b030d7da7

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}
\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, 
\\Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Magherita di Leo$^8$\\ \bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, 
$^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Italy}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}
{
\small \noindent Geographical Information Systems (GIS) is known for its capacity 
to spatially enhance the capacity of man- agement of natural resources. 
While being often used as an analytical tool, it also represents a collaborative 
scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
Thus, a large number of scientific geospatial computations depend on quality and 
correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
helps to preserve reproducibility of scientific results over time as the original author 
designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
improvements are tracked in the source code versioning system and are immediately 
available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
generation of scientists.\vspace{5mm}\newline

@@

A set of modules for multiscale analysis of landscape structure was added in 1992 
by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
improved to become r.li in 2006. Further development continued, with a significant 
speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example 
http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html.\vspace{5mm}\newline

GRASS GIS entails several modules that constitute the result of active research on 
natural hazard. The r.sim.water simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
for overland flow under rainfall excess conditions was integrated into the Emergency 
Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}). 
It was also modified by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of a 
specialised software called Tangible Landscape (previously Tangible GIS), which also 
incorporated the r.damflood module.\vspace{5mm}\newline

The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
functions r.ros and r.spread, is object of active research. It has been extensively 
tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
2013 \cite{rodriguez2013data} ; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
}

>>>>

\title{\bigskip GRASS GIS: a peer-reviewed scientific platform\\ and future research repository\bigskip}

\author{Yann Chemin$^4$, Vaclav Petráš$^3$, Anna Petrášova$^3$, Martin Landa$^2$, Soeren Gebbert$^5$, \\
Pietro Zambelli$^6$, Markus Neteler$^1$, Peter Loewe$^7$, Margherita Di Leo$^8$\\ 
\bigskip
$^1$ CRI, FEM, Italy, $^2$ CTU in Prague, Czech Republic, $^3$ NCSU, USA, $^4$ IWMI, Sri Lanka, 
$^5$ TICSA, Germany, $^6$ EURAC, Italy, $^7$ GNLST, Germany, $^8$ EC-JRC, Italy}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Abstract}
{
\small \noindent Geographical Information Systems (GIS) is known for its capacity 
to spatially enhance the capacity of management of natural resources. 
While being often used as an analytical tool, it also represents a collaborative 
scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
Thus, a large number of scientific geospatial computations depend on quality and 
correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
helps to preserve reproducibility of scientific results over time as the original author 
designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
improvements are tracked in the source code versioning system and are immediately 
available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
generation of scientists.\vspace{5mm}\newline

@@

A set of modules for multiscale analysis of landscape structure was added in 1992 
by Baker et al. \cite{baker1992r}, who developed the r.le model similar to 
FRAGSTATS \cite{mcgarigal1995fragstats}, see manual. The modules were gradually 
improved to become \textit{r.li} in 2006. Further development continued, with a significant 
speed up (Trac1, 2014) and new interactive user interface.\vspace{5mm}\newline
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example 
\textit{http://courses.ncsu.edu/gis582/common/grass/interpolation\_2.html}.
\vspace{5mm}\newline

GRASS GIS entails several modules that constitute the result of active research on 
natural hazard. The \textit{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b}) 
for overland flow under rainfall excess conditions was integrated into the Emergency 
Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}). 
It was also modified by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of a 
specialised software called \textit{Tangible Landscape} (previously \textit{Tangible GIS}), which also 
incorporated the \textit{r.damflood} module.\vspace{5mm}\newline

The wildfire simulation toolset, firstly developed by Xu, 1994 \cite{xu1994simulating}, 
implementing Rothermel’s model \cite{Rothermel1983how}, available through the GRASS 
functions \textit{r.ros} and \textit{r.spread}, is object of active research. It has been extensively 
tested and recently adapted to European fuel types (Rodriguez-Aseretto et al.,
2013 \cite{rodriguez2013data} ; de Rigo et al., 2013 \cite{derigo2013architecture} ; 
Di Leo et al., 2013 \cite{2013_DiLeo_etAl}).
}
